Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-08-10 GWLDCI.tex
fixed my thanks

\title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
\author{Susama Agarwala\thanks{SA was supported by an ONR grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
%\date{}

>>>>

\title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
%\date{}
